\chapter*{Acknowledgements}
This thesis would not have been possible without the guidance and support of many people. 

First, I would like to thank my advisor Dr. Richard Zemel. Dr. Zemel brought me into the research gate of machine learning when I still did not know anything about it. He suggested such an interesting research project to me that I had never believed I could work on it. Throughout the final year of my undergraduate studies, he always encouraged me on any little progress I made. He gave me many new directions and resources that lead to results of this research.

I owe many thanks to my mentor Ryan Kiros, who is a PhD student in the machine learning group. Ryan has spent a lot of time helping me on this thesis, and has inspired me with a lot of his brilliant ideas on the model design. His energetic attitude also influenced me. Without Ryan's guidance, I certainly would not have achieved as many results. 

I also want to thank Dr. Ruslan Salakhutdinov for a helpful discussion on the bidirectional models, and Nitish Srivastava for his support on the Toronto Conv Net. Nitish's excellent Conv Net software and trained models really made my research easy to get started.  Of course, my research would not have been feasible without the computing resources. Dr. Zemel did not have any hesitation assigning me with all the computing resources I needed, and I am thankful to Dr. Relu Patrascu for setting up my account and access to the computing clusters. 

I would like to thank everyone in the machine learning group at the University of Toronto. I benefited a lot from attending the weekly cookie talks and paper discussions. They really broadened my knowledge on the cutting-edge research in the machine learning community.

I would like to say thank you to all of my friends in Engineering Science. I enjoyed the four years of fruitful undergraduate studies with you and I will be very proud of being an Engineering Science alumnus.

Finally, I would like to thank my parents Yue Li and Lizhi Ren. I thank their love and support to let me explore in the area of my interest and passion. 